Unknown

### 2024-04-10 ms/ms.qmd
working on predictions subsection

---
title: Unknown
format:
  pdf:
    keep-tex: true  
    toc: false
header-includes: |
  \usepackage{hyperref}
  \addtokomafont{disposition}{\rmfamily}
  \usepackage{siunitx}
  \newcommand{\aax}{$\mathrm{AA}$}
  \newcommand{\Aamphi}{$A_{\mathrm{amphi}}$}
  \newcommand{\Ahypo}{$A_{\mathrm{hypo}}$}
  \newcommand{\agcurve}{$A \textendash g_\text{sw}$}
  \newcommand{\aqcurve}{$A \textendash Q$}
  \newcommand{\ca}{$C_\mathrm{a}$}
  \newcommand{\caequals}[1]{$C_\mathrm{a} = \qty{#1}{\micro\mol\raiseto{-1}\mol}$}
  \newcommand{\cabetween}[2]{#1 < $C_\mathrm{a} < \qty{#2}{\micro\mol\raiseto{-1}\mol}$}
  \newcommand{\gsw}{$g_\text{sw}$}
  \newcommand{\loggsw}{$\log(g_\text{sw})$}
  \newcommand{\logA}{$\log(A)$}
  \newcommand{\ppfd}{$\mathrm{PPFD}$}
  \newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
  \newcommand{\ppfdqty}[1]{$\qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
  \newcommand{\rh}{$\mathrm{RH}$}
  \newcommand{\rhequals}[1]{$\mathrm{RH} = #1\%$}
  \newcommand{\tleafequals}[1]{$T_\mathrm{leaf} = \qty{#1}{\degreeCelsius}$}
mainfont: Times New Roman
bibliography: solanum-aa.bib
csl: https://www.zotero.org/styles/science
---

@@

#### Fitting models in *Stan*

@@

Within the $k^{\text{th}}$ leaf, we estimated \aax{} for each light intensity by integrating the difference in \logA between the amphi and pseudohypo \agcurve{} curves over the range of \gsw{} values where the curves overlap (from $\min(\log(g_\text{sw}))$ to $\max(\log(g_\text{sw}))$). The estimate of \aax{} for the $k^{\text{th}}$ leaf at light intensity $l$ in accession $m$ is:

@@

$$\theta_\text{hypo} \in \{\hat{b}_{0, f(\text{hypo}, k,l,m)}, \hat{b}_{1, f(\text{hypo}, k,l,m)}, \hat{b}_{2, f(\text{hypo}, k,l,m)}\}.$$ 
The function $f : \Theta_1 \rightarrow \Theta_2$ maps the set $\Theta_1$ indexed by leaf type (amphi or pseudohypo), leaf replicate, light intensity, and accession to set $\Theta_2$ indexed by individual \agcurve{} curve. This mapping is necessary because the random effects structure differs between models of \loggsw on \logA and that of models predicting \aax{} described in the next section.

@@

We estimated these parameters for each leaf using the posterior distribution of the parameters from the \agcurve{} curve fitting procedure.

#### Predictions

@@

We tested competing predictions through a combination of model selection and parameter estimation from the posterior of selected models. We started with a base model that includes fixed effects of light intensity and light treatment on \aax, a random effect of accession on \aax, and a linear regression of PAR on accession-level \aax. We next compared the fit of the base model to a more complex with an interaction between light intensity and light treatment using LOOIC with the \textit{R} package **loo** version `r packageVersion("loo")` [@vehtari_practical_2017]. These comparisons allowed us to test the main predictions of each hypothesis and for a reinforcing interactions between assimilatory and plastic hypotheses (tab:predictions). However, these models cannot test predictions when there is an interaction with the constitutive hypothesis, because this hypothesis posits accession-levels variation in responses to light intensity and/or light treatment. Therefore, we tested for significant variation among accessions in light intensity and light treatment by comparing LOOIC values of models with and without random interactions between these factors and accession.

>>>>

---
title: Unknown
format:
  pdf:
    keep-tex: true  
    toc: true
number-sections: true
header-includes: |
  \usepackage{hyperref}
  \addtokomafont{disposition}{\rmfamily}
  \usepackage{siunitx}
  \newcommand{\aax}{$\mathrm{AA}$}
  \newcommand{\Aamphi}{$A_{\mathrm{amphi}}$}
  \newcommand{\Ahypo}{$A_{\mathrm{hypo}}$}
  \newcommand{\agcurve}{$A \textendash g_\text{sw}$}
  \newcommand{\aqcurve}{$A \textendash Q$}
  \newcommand{\ca}{$C_\mathrm{a}$}
  \newcommand{\caequals}[1]{$C_\mathrm{a} = \qty{#1}{\micro\mol\raiseto{-1}\mol}$}
  \newcommand{\cabetween}[2]{#1 < $C_\mathrm{a} < \qty{#2}{\micro\mol\raiseto{-1}\mol}$}
  \newcommand{\gsw}{$g_\text{sw}$}
  \newcommand{\loggsw}{$\log(g_\text{sw})$}
  \newcommand{\logA}{$\log(A)$}
  \newcommand{\ppfd}{$\mathrm{PPFD}$}
  \newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
  \newcommand{\ppfdqty}[1]{$\qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
  \newcommand{\rh}{$\mathrm{RH}$}
  \newcommand{\rhequals}[1]{$\mathrm{RH} = #1\%$}
  \newcommand{\tleafequals}[1]{$T_\mathrm{leaf} = \qty{#1}{\degreeCelsius}$}
mainfont: Times New Roman
bibliography: solanum-aa.bib
csl: https://www.zotero.org/styles/science
---

@@

#### Fitting models in *Stan* {#sec-fitting}

@@

Within the $k^{\text{th}}$ leaf, we estimated \aax{} for each light intensity by integrating the difference in \logA{} between the amphi and pseudohypo \agcurve{} curves over the range of \gsw{} values where the curves overlap (from $\min(\log(g_\text{sw}))$ to $\max(\log(g_\text{sw}))$). The estimate of \aax{} for the $k^{\text{th}}$ leaf at light intensity $l$ in accession $m$ is:

@@

$$\theta_\text{hypo} \in \{\hat{b}_{0, f(\text{hypo}, k,l,m)}, \hat{b}_{1, f(\text{hypo}, k,l,m)}, \hat{b}_{2, f(\text{hypo}, k,l,m)}\}.$$ 
The function $f : \Theta_1 \rightarrow \Theta_2$ maps the set $\Theta_1$ indexed by leaf type (amphi or pseudohypo), leaf replicate, light intensity, and accession to set $\Theta_2$ indexed by individual \agcurve{} curve. This mapping is necessary because the random effects structure differs between models of \loggsw{} on \logA{} and that of models predicting \aax{} described in the next section.

@@

#### Predictions {#sec-predictions}

The assimilatory, plastic, and constitutive hypotheses make different predictions about the relationship between \aax{} and light intensity, light treatment, and native \ppfd{} among accessions. Since these hypotheses are not mutually exclusive, we describe how we assessed support for one, two, or all three hypotheses simultaneously in \autoref{tbl-predictions}.

We evaluated predictions using a combination of parameter estimation and model selection. In all cases, we estimated parameters and confidence intervals as described in @sec-fitting. If the 95% confidence intervals for a parameter did not overlap zero, we considered the parameter to be significantly different from zero. We used leave-one-out cross-validation (LOOIC) to compare the fit of models (\autoref{tbl-models}) using the *R* package **loo** version `r packageVersion("loo")` [@vehtari_practical_2017] to calculate LOOIC values. We considered models with two standard errors of the mean lower LOOIC value to be a better fit to the data; we considered models with LOOIC values within two standard errors of the mean to be have similar support.

```{r, predictions, eval=FALSE, echo=FALSE,message=FALSE,warning=FALSE}
#| label: tbl-predictions
#| tbl-cap: "caption"

@@

### 2024-04-10 ms/ms.tex
working on predictions subsection

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\subsection{Notes}\label{notes}

@@

\subsection{Authors}\label{authors}

@@

\subsection{Main}\label{main}

@@

\subsection{Materials and Methods}\label{materials-and-methods}

@@

\subsubsection{Accessions}\label{accessions}

@@

\subsubsection{Plant growth conditions}\label{plant-growth-conditions}

@@

\paragraph{Germination and seedling
stage}\label{germination-and-seedling-stage}

@@

\paragraph{Light treatments}\label{light-treatments}

@@

\subsubsection{Leaf trait measurements}\label{leaf-trait-measurements}

@@

\paragraph{Amphistomy advantage}\label{amphistomy-advantage}

@@

\paragraph{\texorpdfstring{Light-response (\aqcurve)
curves}{Light-response () curves}}\label{light-response-curves}

@@

\paragraph{Stomatal anatomy}\label{stomatal-anatomy}

@@

\paragraph{Leaf mass per area}\label{leaf-mass-per-area}

@@

\subsubsection{\texorpdfstring{Cleaning \agcurve{}
curves}{Cleaning  curves}}\label{cleaning-curves}

@@

\paragraph{Remove unreliable and unusable data
points}\label{remove-unreliable-and-unusable-data-points}

@@

\paragraph{\texorpdfstring{Remove hysteretic portion of \agcurve{}
curves at low
\gsw{}}{Remove hysteretic portion of  curves at low }}\label{remove-hysteretic-portion-of-curves-at-low}

@@

\paragraph{\texorpdfstring{Remove outliers within each \agcurve{}
curve}{Remove outliers within each  curve}}\label{remove-outliers-within-each-curve}

@@

\paragraph{\texorpdfstring{Thin redundant data points within each
\agcurve{}
curve}{Thin redundant data points within each  curve}}\label{thin-redundant-data-points-within-each-curve}

@@

\paragraph{\texorpdfstring{Remove replicates with no overlap between
amphi and pseudohypo \agcurve{}
curves}{Remove replicates with no overlap between amphi and pseudohypo  curves}}\label{remove-replicates-with-no-overlap-between-amphi-and-pseudohypo-curves}

@@

\paragraph{\texorpdfstring{Trim extreme \aax{}
values}{Trim extreme  values}}\label{trim-extreme-values}

@@

\subsubsection{\texorpdfstring{Cleaning \aqcurve{}
curves}{Cleaning  curves}}\label{cleaning-curves-1}

@@

\paragraph{\texorpdfstring{Remove outliers within each \aqcurve{}
curve}{Remove outliers within each  curve}}\label{remove-outliers-within-each-curve-1}

@@

\paragraph{\texorpdfstring{Remove \aqcurve{} curves with poor
fit}{Remove  curves with poor fit}}\label{remove-curves-with-poor-fit}

@@

\subsubsection{\texorpdfstring{Bayesian data analysis in
\emph{Stan}}{Bayesian data analysis in Stan}}\label{bayesian-data-analysis-in-stan}

@@

\paragraph{\texorpdfstring{Fitting models in
\emph{Stan}}{Fitting models in Stan}}\label{fitting-models-in-stan}

@@

\paragraph{Parameter estimation and
priors}\label{parameter-estimation-and-priors}

@@

\subparagraph{\texorpdfstring{\agcurve{} curve
parameters}{ curve parameters}}\label{curve-parameters}

@@

\subparagraph{\texorpdfstring{\aax{} for each light intensity with leaf
using \agcurve{} curve
parameters}{ for each light intensity with leaf using  curve parameters}}\label{for-each-light-intensity-with-leaf-using-curve-parameters}

Within the \(k^{\text{th}}\) leaf, we estimated \aax{} for each light
intensity by integrating the difference in \logA between the amphi and
pseudohypo \agcurve{} curves over the range of \gsw{} values where the
curves overlap (from \(\min(\log(g_\text{sw}))\) to
\(\max(\log(g_\text{sw}))\)). The estimate of \aax{} for the
\(k^{\text{th}}\) leaf at light intensity \(l\) in accession \(m\) is:

@@

\[\theta_\text{hypo} \in \{\hat{b}_{0, f(\text{hypo}, k,l,m)}, \hat{b}_{1, f(\text{hypo}, k,l,m)}, \hat{b}_{2, f(\text{hypo}, k,l,m)}\}.\]
The function \(f : \Theta_1 \rightarrow \Theta_2\) maps the set
\(\Theta_1\) indexed by leaf type (amphi or pseudohypo), leaf replicate,
light intensity, and accession to set \(\Theta_2\) indexed by individual
\agcurve{} curve. This mapping is necessary because the random effects
structure differs between models of \loggsw on \logA and that of models
predicting \aax{} described in the next section.

\subparagraph{\texorpdfstring{Effects of light intensity, light
treatment, and accession on
\aax}{Effects of light intensity, light treatment, and accession on }}\label{effects-of-light-intensity-light-treatment-and-accession-on}

@@

\subparagraph{\texorpdfstring{Effects of native light habitat on
accession-level
\aax}{Effects of native light habitat on accession-level }}\label{effects-of-native-light-habitat-on-accession-level}

@@

We estimated these parameters for each leaf using the posterior
distribution of the parameters from the \agcurve{} curve fitting
procedure.

\paragraph{Predictions}\label{predictions}

@@

We tested competing predictions through a combination of model selection
and parameter estimation from the posterior of selected models. We
started with a base model that includes fixed effects of light intensity
and light treatment on \aax, a random effect of accession on \aax, and a
linear regression of PAR on accession-level \aax. We next compared the
fit of the base model to a more complex with an interaction between
light intensity and light treatment using LOOIC with the \textit{R}
package \textbf{loo} version 2.7.0 (\emph{15}). These comparisons
allowed us to test the main predictions of each hypothesis and for a
reinforcing interactions between assimilatory and plastic hypotheses
(tab:predictions). However, these models cannot test predictions when
there is an interaction with the constitutive hypothesis, because this
hypothesis posits accession-levels variation in responses to light
intensity and/or light treatment. Therefore, we tested for significant
variation among accessions in light intensity and light treatment by
comparing LOOIC values of models with and without random interactions
between these factors and accession.

@@

\subsection{Acknowledgements}\label{acknowledgements}

@@

\subsection*{References}\label{references}
\addcontentsline{toc}{subsection}{References}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\section{Notes}\label{notes}

@@

\section{Authors}\label{authors}

@@

\section{Main}\label{main}

@@

\section{Materials and Methods}\label{materials-and-methods}

@@

\subsection{Accessions}\label{accessions}

@@

\subsection{Plant growth conditions}\label{plant-growth-conditions}

@@

\subsubsection{Germination and seedling
stage}\label{germination-and-seedling-stage}

@@

\subsubsection{Light treatments}\label{light-treatments}

@@

\subsection{Leaf trait measurements}\label{leaf-trait-measurements}

@@

\subsubsection{Amphistomy advantage}\label{amphistomy-advantage}

@@

\subsubsection{\texorpdfstring{Light-response (\aqcurve)
curves}{Light-response () curves}}\label{light-response-curves}

@@

\subsubsection{Stomatal anatomy}\label{stomatal-anatomy}

@@

\subsubsection{Leaf mass per area}\label{leaf-mass-per-area}

@@

\subsection{\texorpdfstring{Cleaning \agcurve{}
curves}{Cleaning  curves}}\label{cleaning-curves}

@@

\subsubsection{Remove unreliable and unusable data
points}\label{remove-unreliable-and-unusable-data-points}

@@

\subsubsection{\texorpdfstring{Remove hysteretic portion of \agcurve{}
curves at low
\gsw{}}{Remove hysteretic portion of  curves at low }}\label{remove-hysteretic-portion-of-curves-at-low}

@@

\subsubsection{\texorpdfstring{Remove outliers within each \agcurve{}
curve}{Remove outliers within each  curve}}\label{remove-outliers-within-each-curve}

@@

\subsubsection{\texorpdfstring{Thin redundant data points within each
\agcurve{}
curve}{Thin redundant data points within each  curve}}\label{thin-redundant-data-points-within-each-curve}

@@

\subsubsection{\texorpdfstring{Remove replicates with no overlap between
amphi and pseudohypo \agcurve{}
curves}{Remove replicates with no overlap between amphi and pseudohypo  curves}}\label{remove-replicates-with-no-overlap-between-amphi-and-pseudohypo-curves}

@@

\subsubsection{\texorpdfstring{Trim extreme \aax{}
values}{Trim extreme  values}}\label{trim-extreme-values}

@@

\subsection{\texorpdfstring{Cleaning \aqcurve{}
curves}{Cleaning  curves}}\label{cleaning-curves-1}

@@

\subsubsection{\texorpdfstring{Remove outliers within each \aqcurve{}
curve}{Remove outliers within each  curve}}\label{remove-outliers-within-each-curve-1}

@@

\subsubsection{\texorpdfstring{Remove \aqcurve{} curves with poor
fit}{Remove  curves with poor fit}}\label{remove-curves-with-poor-fit}

@@

\subsection{\texorpdfstring{Bayesian data analysis in
\emph{Stan}}{Bayesian data analysis in Stan}}\label{bayesian-data-analysis-in-stan}

@@

\subsubsection{\texorpdfstring{Fitting models in
\emph{Stan}}{Fitting models in Stan}}\label{sec-fitting}

@@

\subsubsection{Parameter estimation and
priors}\label{parameter-estimation-and-priors}

@@

\paragraph{\texorpdfstring{\agcurve{} curve
parameters}{ curve parameters}}\label{curve-parameters}

@@

\paragraph{\texorpdfstring{\aax{} for each light intensity with leaf
using \agcurve{} curve
parameters}{ for each light intensity with leaf using  curve parameters}}\label{for-each-light-intensity-with-leaf-using-curve-parameters}

Within the \(k^{\text{th}}\) leaf, we estimated \aax{} for each light
intensity by integrating the difference in \logA{} between the amphi and
pseudohypo \agcurve{} curves over the range of \gsw{} values where the
curves overlap (from \(\min(\log(g_\text{sw}))\) to
\(\max(\log(g_\text{sw}))\)). The estimate of \aax{} for the
\(k^{\text{th}}\) leaf at light intensity \(l\) in accession \(m\) is:

@@

\[\theta_\text{hypo} \in \{\hat{b}_{0, f(\text{hypo}, k,l,m)}, \hat{b}_{1, f(\text{hypo}, k,l,m)}, \hat{b}_{2, f(\text{hypo}, k,l,m)}\}.\]
The function \(f : \Theta_1 \rightarrow \Theta_2\) maps the set
\(\Theta_1\) indexed by leaf type (amphi or pseudohypo), leaf replicate,
light intensity, and accession to set \(\Theta_2\) indexed by individual
\agcurve{} curve. This mapping is necessary because the random effects
structure differs between models of \loggsw{} on \logA{} and that of
models predicting \aax{} described in the next section.

\paragraph{\texorpdfstring{Effects of light intensity, light treatment,
and accession on
\aax}{Effects of light intensity, light treatment, and accession on }}\label{effects-of-light-intensity-light-treatment-and-accession-on}

@@

\paragraph{\texorpdfstring{Effects of native light habitat on
accession-level
\aax}{Effects of native light habitat on accession-level }}\label{effects-of-native-light-habitat-on-accession-level}

@@

\subsubsection{Predictions}\label{sec-predictions}

WORKING HERE TO ADD PREDICTIONS AND TABLE

The assimilatory, plastic, and constitutive hypotheses make different
predictions about the relationship between \aax{} and light intensity,
light treatment, and native \ppfd{} among accessions. Since these
hypotheses are not mutually exclusive, we describe how we assessed
support for one, two, or all three hypotheses simultaneously.

We tested competing predictions through a combination of model selection
and parameter estimation from the posterior of fitted models. In all
cases, we estimated parameters and confidence intervals as described in
Section~\ref{sec-fitting}.

We started with a base model that includes fixed effects of light
intensity and light treatment on \aax, a random effect of accession on
\aax, and a linear regression of PAR on accession-level \aax. We next
compared the fit of the base model to a more complex with an interaction
between light intensity and light treatment using LOOIC with the
\textit{R} package \textbf{loo} version 2.7.0 (\emph{15}). These
comparisons allowed us to test the main predictions of each hypothesis
and for a reinforcing interactions between assimilatory and plastic
hypotheses (tab:predictions). However, these models cannot test
predictions when there is an interaction with the constitutive
hypothesis, because this hypothesis posits accession-levels variation in
responses to light intensity and/or light treatment. Therefore, we
tested for significant variation among accessions in light intensity and
light treatment by comparing LOOIC values of models with and without
random interactions between these factors and accession.

@@

@@

\section{Acknowledgements}\label{acknowledgements}

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}
